Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
added the configuration dialog figure

>>>>

\begin{figure}[t]
  \centering
    \includegraphics[width=0.5\textwidth]{configuration-screenshot.png}
    \caption{The Tor Bridges Configuration window of the Tor configuration interface. Tor users in censored environments and some of our participants will be required to select the correct bridge for circumventing censorship. Note that the interface prompts users to choose a transport type, which can be the source of confusion. Bridges are non-listed guard relays to the Tor network, and some of them can have transport types which obfuscate traffic in different ways.}
\end{figure}
